% !TEX root=../main.tex
%%参考文献
\addcontentsline{toc}{chapter}{\numberline{}参考文献}
\label{chap:bibliography}
\markright{参考文献}
%%月名の略し方
%%Jan. Feb. March April May June July Aug. Sep(t). Oct. Nov. Dec.

%\begin{thebibliography}{9}  %%文献数が10未満のとき
\begin{thebibliography}{99}  %%文献数が10以上のとき

 %%雑誌：著者名，``標題，''雑誌名，巻，号，pp.**--**, 月 年.
\bibitem{skin1}
Ilker Ali OZKAN , Murat KOKLU,"Skin Lesion Classification using Machine Learning Algorithms",IJISAE, 2017, 5(4), p.285–289 

\bibitem{skin2}
A. Esteva, B. Kuprel, R. A. Novoa, J. Ko, S. M. Swetter, H. M. Blau,
and S. Thrun,"Dermatologist-level classification of skin cancer with
deep neural networks,"Nature, vol. 542, no. 7639, pp. 115–118, 2017

\bibitem{skin3}
American Cancer Society，"Cancer Facts \& Figures 2016"

\bibitem{VGG16}
	Karen Simonyan, and Andrew Zisserman,
	 “Very deep convolutional networks for large-scale image recognition”, 
	arXiv preprint arXiv:1409.1556, 2014.
    
\bibitem{ResNet}
	Kaiming He, Xiangyu Zhang, Shaoqing Ren and Jian Sun,
	“Deep residual learning for image recognition”,
	 IEEE Conference on Computer Vision and Pattern Recognition, 2016.

\bibitem{AlexNet}
	 Alex Krizhevsky, Ilya Sutskever, and Geoffrey E. Hinton,
 	“Imagenet classification with deep convolutional neural networks”,
	Advances in neural information processing systems, 2012.

\bibitem{Faster RCNN}
	Shaoqing Ren, Kaiming He, Ross Girshick, and Jian Sun,
	“Faster R-CNN: Towards real-time object detection with region proposal networks”, 
	Advances in neural information processing systems, pp. 91–99, 2015.



 %%著書・編書：著者名，書名，編者名，発行所，発行都市名，発行年.
 %\bibitem{Handbook}
%	 高木幹雄，下田陽久（監修），
%	 新編画像解析ハンドブック，
%	 東京大学出版会，東京，2004.
 %%著書の一部を引用する場合
	 %
	 %
	 %
 %%国際会議：著者名, ``標題,'' 会議名, (no.論文番号,) pp.**--**, 開催都市名，国名，月 年.

\end{thebibliography}